\large{\bf Large effects and the infinitesimal model }

### 2023-07-08 writeup.tex
.

Since $\varphi$ and $\Phi$ are characteristic functions, they are absolutely continuous and $\phi(0) = \Phi(0) = 1$, and thus both are non-zero in a neighbourhood of 0. In particular, $\psi(\theta) = \Log{\varphi}(\theta)$ and $\Psi(\theta) = \Log{\Phi(\theta)}$ exist in some neighbourhood of 0 as well\footnote{We use $\Log$ to denote the principal value of the complex logarithm, for which the imaginary part always lies in the interval $(-\pi,\pi]$.}.  From the above, we have
\[
	\Log{F^{(n)}(\varphi)(\theta)} = {\textstyle 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)} 
		+ \sum_{k=1}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}.
\]
We briefly explore what possible limiting values are valid characteristic functions.  We refer to the first term on the left hand side as the \emph{reproduction term} and the remaining sum as the \emph{noise term}, and only consider to the case when both have well-posed limits independent of the other.

\paragraph{Noise Terms}
First, consider the noise terms.  A necessary condition for $\sum_{k=1}^{\infty} 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)$ to converge is that $2^{k} \Psi\left(\frac{\theta}{2^{k}}\right) \to 0$; since $\Psi(0) = 0$, this implies that if it exists, $\Psi'(0+) = 0$.  In particular, as we would expect, if $R$ has a mean, it must be 0.  If, on the other hand, $\Psi(\theta)$ is twice differentiable, so $R$ has mean 0 and finite variance, say $\Psi''(0) = \eta^{2}$.  Taylor's theorem then tells us that for $\theta$ sufficiently small, 
\[
	\Psi(\theta) \frac{\eta^{2}}{2} \theta^{2} + r(\theta)\theta^{2},
\]
where $r(\theta) \to 0$ as $\theta \to 0$.  Thus,
\begin{equation*}
	\frac{\textstyle 2^{k+1} \Psi\left(\frac{\theta}{2^{k+1}}\right)}{\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}
	= \frac{1}{2} \frac{\eta^{2} \theta^{2} + {\textstyle  r\left(\frac{\theta}{2^{k+1}}\right)}\theta^{2}}{\eta^{2} \theta^{2} + {\textstyle  r\left(\frac{\theta}{2^{k}}\right)}\theta^{2}}
	\to \frac{1}{2},
\end{equation*}
as $k \to \infty$ and the sum converges by the ratio test.  In this case,
\begin{align*}
	 \sum_{k=1}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}
	 &=  \sum_{k=1}^{n-1} 2^{k} {\textstyle \left(- \frac{\eta^{2}}{2}  \frac{\theta^{2}}{2^{2k}}
		+ r\left(\frac{\theta}{2^{k}}\right)\frac{\theta^{2}}{2^{2k}}\right)}\\
	&=- \eta^{2} \theta^{2} (1 - 2^{-n+1})  + \sum_{k=1}^{n-1} {\textstyle r\left(\frac{\theta}{2^{k}}\right)\frac{\theta^{2}}{2^{k}}}
\end{align*}
If we assume that $r(\theta) \equiv 0$, so that the noise is $N(0,\eta^{2})$, then the limiting distribution is $N(0,2\eta^{2})$. Note that when  $r(\theta)$ is non-zero, we don't expect the higher order terms to vanish.

@@

\paragraph{Reproductive Terms:}
We now turn our attention to the limit
\[
		\alpha(\theta) = \lim_{n \to \infty} 2^{n}\psi\left(\frac{\theta}{2^{n}}\right)
\]
If it exists, then for all integers $k$, 
\[
	\alpha(2^{k} \theta) = \lim_{n \to \infty} 2^{n}\psi\left(\frac{2^{k} \theta}{2^{n}}\right) =  \lim_{n \to \infty} 2^{k} 2^{n-k} \psi\left(\frac{\theta}{2^{n-k}}\right) = 2^{k} \alpha(\theta).
\]
and, since $\alpha(0) = 0$,
\[
	\frac{\alpha(\theta)}{\theta} = \frac{\alpha(2^{k} \theta)}{2^{k}\theta} 
	\to \begin{cases} 
		\alpha'(0+) & \text{if $\theta > 0$, and}\\
		\alpha'(0-) & \text{if $\theta < 0$,}
	\end{cases}
\]
as $k \to - \infty$ if the limits exist (\ie there are unique left-and right-hand limit at zero; this is the case if \eg we require $\alpha(\theta)$, and thus $\phi(\theta)$, to be convex functions).  We henceforth assume this.

Since $\varphi(\theta)$ is a characteristic function, it has the Hermitian property: $\phi(-\theta) = \overline{\phi(\theta)}$, and thus $\psi(-\theta) = \overline{\psi(\theta)}$ and $\alpha(-\theta) = \overline{\alpha(\theta)}$.  In particular, if one (and by extension both) limits exist, we must have $\alpha'(0-) = \overline{\alpha'(0+)}$.  In this case, setting $-\gamma + i m = \alpha'(0+)$, we have
\[
	\alpha(\theta) = \begin{cases} 
		i m\theta - \gamma \theta & \text{if $\theta \geq 0$, and}\\
		i m\theta + \gamma \theta & \text{if $\theta < 0$}.
	\end{cases}
\]
If $\gamma > 0$, then we recognize $e^{\alpha(\theta)} = e^{im \theta -\gamma|\theta|}$ as the characteristic function of a Cauchy distribution with median 0 and mean absolute deviation $\gamma$, whereas if $\gamma = 0$, then $e^{\alpha(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.    In general, it does not seem possible to exclude $\gamma < 0$. However, recalling that if $\phi(\theta)$ is the characteristic function of a random variable $Z$, Jensen's inequality tells us that for all $\theta$,
\begin{equation}\label{eq:CF-J}
	|\phi(\theta)| = \left|\E\left[e^{i\theta Z}\right]\right| \leq \E\left[\left|e^{i\theta Z}\right|\right] = 1,
\end{equation}
we can conclude $\gamma \geq 0$ when the limiting noise term is a mixture of Gaussians and stable laws of the form \eqref{eq:stablenoises}: we then have 
\[
	|\phi(\theta)| = e^{\re(\alpha(\theta) + o(|\theta|))} = e^{\gamma |\theta| + o(|\theta|))},
\] 
and thus is less than or equal to one in a small neighbourhood of $0$ if and only if $\gamma < 0$.

\paragraph{Lamarkian inheritance redux.} 
Note that the characteristic functions constructed above are solutions to \eqref{eq:CF_neutral} when transmission is noiseless, and the offspring have exactly the parental mean trait -- \ie Lamarkian blending inheritance.  The solution $\phi(\theta) = e^{i\theta m}$ is exactly the reversion to the mean that Darwin's detractors used to argue against the theory of evolution \citep{Provine1971}.  The solution $\phi(\theta) = e^{im \theta -\gamma|\theta|}$ offers an amusing counter-factual: if a Lamarkian population could somehow achieved a Cauchy-distributed trait distribution, it would maintain that diversity indefinitely.

@@

\paragraph{Gaussian Solution:}
First, consider the case when $\mu(x) = e^{a x^{2}}$.   In this case there is a Gaussian solution: suppose $Z$ is Gaussian with mean $m$ and variance $\sigma^{2}$.  Then,
$ \phi(\theta) = \exp(i m \theta - \frac{1}{2} \sigma^{2} \theta^{2}).  $
Moreover, provided $a < \frac{1}{2\sigma^{2}}$, we can explicitly compute $\frac{\mathbb{E}\left[e^{i \theta Z}\mu(Z)\right]}{\mathbb{E}[\mu(Z)]}$  using the Gaussian probability density function to conclude that
if $R$ is Gaussian with mean zero and variance $\eta^2$, then equation~\eqref{eqn:MSB_CF} becomes
\[
	e^{i m \theta - \frac{1}{2} \left(\frac{\sigma^{2}}{2} + \eta^{2}\right)\theta^{2}}
	= e^{i \frac{m}{1-2 a \sigma^{2}}\theta 
		- \frac{1}{2} \frac{\sigma^{2}}{1-2 a \sigma^{2}}\theta^{2}},
\]
which, equating real and complex components, has a solution provided $m = 0$ and
\[
	\sigma^{2} = \frac{\sqrt{16 a^{2} \eta^{4} + 24 a \eta^{2}+1} - 4a \eta^{2} -1}{4a} 
	=  2\eta^{2}(1-4a\eta^{2}) + O(a^{2}).
\]

Note that we do not require very weak selection to guarantee a Gaussian steady state, only that $a < \frac{1}{2\sigma^{2}}$.  However, this does not imply that the transient distribution is also Gaussian, as is sometimes assumed \citep[e.g.,][]{lande1976natural}. %  The latter does indeed require very weak selection.

@@

Above we have seen that
(a) in principle,
a mutation-selection balance is possible with a Cauchy empirical distribution and Cauchy Mendelian sampling term,
but (b)
such a model cannot derive from a simple model with additive loci.
To that end, it's instructive to see where the argument of \cite{barton2017infinitesimal} breaks down
if instead of assuming bounded allele effects of order $\Oh\left(1/\sqrt{M}\right)$,
we assume that the allele at locus $i$ in individual $j$ contributes
$\eta^{[j]}_{\ell}/M$, where the $\eta^{[j]}_{\ell}$ are independent $\Cauchy(0,\gamma_{\ell})$ random variables. 
In this case, the typical effect size at locus $\ell$ is of order $\frac{\gamma_{\ell}}{M}$,
which is asymptotically smaller than the allele effects assumed in \cite{barton2017infinitesimal},
but large effect alleles are more likely.

@@

The key observation is this:
while is meaningless to speak of variances when the Mendelian sampling term is $\alpha$-stable, if an individual's trait value is informative of the allelic effect at any given locus,
then its trait value is informative of the \emph{distribution} of an offsprings' trait value,
and hence there can be no independence between parental traits and the Mendelian sampling term
that is central to the tractability of the infinitesimal model.

@@

To see what knowing the parental trait value $Z^{[j]}_{M}$ tells us about the contribution of any given locus, $\eta^{[j]}_{\ell}$, we follow the arguments in  \citet{Fisher1918} and \citet{barton2017infinitesimal} using Bayes' Theorem. Proceeding informally, with the probabilities indicating probability density functions, we have 
\begin{align*}
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\} &= \frac{\P\{\eta^{[j]}_{\ell} = y; Z^{[j]} = z\}}{\P\{Z^{[j]} = z\}}\\
        &= \frac{\P\{Z^{[j]} = z\vert\eta^{[j]}_{\ell} = y\}}{\P\{Z^{[j]} = z\}}\P\{\eta^{[j]}_{\ell} = y\}\\
        &=  \frac{\P\{Z^{[j]} -\frac{1}{M} \eta^{[j]}_{\ell} = z - \frac{1}{M} y\}}{\P\{Z^{[j]} = z\}}\P\{\eta^{[j]}_{\ell} = y\}\\
\end{align*}
Now, $Z^{[j]} -\frac{1}{M} \eta^{[j]}_{\ell} = \frac{1}{M} \sum_{k = 1 : k \neq i}^{M} \eta^{[j]}_{k}$ is Cauchy-distributed with scale $\bar{\gamma} - \frac{\gamma_{\ell}}{M}$.  Using the probability density function for a Cauchy distributed random variable \eqref{eq:Cpdf}, a straightforward computation gives
\begin{align*}
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\}
    &=
    \frac{f\left(z - \frac{y}{M} ;0,\bar{\gamma}-\frac{\gamma_{\ell}}{M}\right)}{f(z;0,\bar{\gamma})} \P\{\eta^{[j]}_{\ell} = y\}\\
    &=
    \left(1
        +
        \frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})}
        \frac{1}{M}
        + \Oh\left(\frac{1}{M^{2}}\right)\right)
        \P\{\eta^{[j]}_{\ell} = y\}.
\end{align*} 
Noting that $|(\bar{\gamma}^2 - z^2)/(\bar{\gamma}^2 + z^2)| \le 1$
and $|z/(\bar{\gamma}^2 + z^2)| \le 1/(2 \bar{\gamma})$
(since it is maximized at $z = \bar{\gamma}$),
so
\begin{align*}
        \left|
        \frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})}
        \right|
        \le \frac{|y|}{\gamma_\ell \bar{\gamma}} ,
\end{align*}
% % BEGIN PREVIOUS ARGUMENT
% Now, as $z \to 0$, $\frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})} \to \frac{\gamma_{\ell}}{\bar{\gamma}}$ and as $z \to \pm \infty$, $\frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})} \to -\frac{\gamma_{\ell}}{\bar{\gamma}}$,  whereas $|\frac{\bar{\gamma}^{2}-z^{2}+2zy}{\bar{\gamma}^{2}+z^{2}}|$ attains a maximum of
% \[
% 	\frac{(\gamma_{\ell}^{2}+y^{2})\left(\sqrt{\gamma_{\ell}^{2}+y^{2}}-\gamma_{\ell}\right)}{\bar{\gamma}(\gamma_{\ell}^{2}+y^{2} - \gamma_{\ell}\sqrt{\gamma_{\ell}^{2}+y^{2}})},
% \]
% which is asymptotically equal to $\frac{|y|}{\bar{\gamma}}$ for large values of $|y|$, at
% \[
% 	z = -\frac{\bar{\gamma}}{y}(\gamma_{\ell} \pm \sqrt{\gamma_{\ell}^{2}+y^{2}}),  
% \]
% which is itself asymptotically equal to $\mp \sgn(y) \bar{\gamma}$ for large values of $|y|$.
% 	
we have that
\[
    \left|
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\} - \P\{\eta^{[j]}_{\ell} = y\}
    \right|
    \le \left(\frac{|y|}{\gamma_\ell \bar{\gamma} M} + \Oh\left(\frac{1}{M^2}\right)\right)  \P\{\eta^{[j]}_{\ell} = y\}.
\]
% Unlike the case of bounded allelic effects, the bound is independent of the trait value $Z^{[j]}$. 
In the case of bounded allelic effects, the error introduced by approximating the effect-size distribution conditional on the trait value by the unconditioned distribution is proportional to $|Z^{[j]}|$, so that extreme trait values are most informative of the size of allelic effects,
whereas here,
the bound is independent of the trait value,
and the error is maximized when the trait value is approximately equal to
the mean absolute deviation of its distribution, \ie the median value of $|Z^{[j]}|$.

@@

\begin{figure}
    \begin{center}
        \includegraphics{sims/neutral_seg_noise}
    \end{center}
    \caption{
        Segregation noise with Gaussian \textbf{(A-C)} and Cauchy \textbf{(D-F)} effect size distributions,
        from the same simulations shown in Figure~\ref{fig:trait_distrns},
        for all individuals born during the last 1,000 time units of the simulation.
        \textbf{(A,D)} Segregation noise (offspring trait minus midparent) plotted against midparent.
        \textbf{(B,E)} Histograms of the Mendelian sampling term.
        \textbf{(B,E)} Enrichment in quantiles of the Mendelian sampling term conditional on midparent value.
        To compute the latter,
        let $q_0, q_2, q_4, \ldots, q_{98}, q_{100}$ divide the distribution of the Mendelian sampling term
        into 50 bins with roughly equal numbers in each (i.e., the quantiles),
        let $p_k(a,b)$ denote the proportion of the offspring of parents with midparent value
        is in $[a, b)$ whose Mendelian sampling term is in $[q_{k-1}, q_k)$,
        and let $p_k$ be the proportion of all offspring with segregation noise in $[q_{k-1}, q_k)$
        (so, $p_k \approx 0.02$).
        Then, each line shows $p_k(a,b)/p_k$
        plotted against the midpoint of the corresponding quantile bin $(q_{k-1},q_k)$,
        for $(a,b)$ chosen to span the 5\% of midparents centered on:
        (red) the 10\% quantile,
        (black) the median, and
        (green) the 90\% quantile of midparent value.
        \label{fig:seg_noise}
    }
\end{figure}

>>>>

Since $\varphi$ and $\Phi$ are characteristic functions, they are continuous and $\phi(0) = \Phi(0) = 1$, and thus both are non-zero in a neighbourhood of 0. In particular, $\psi(\theta) = \Log{\varphi}(\theta)$ and $\Psi(\theta) = \Log{\Phi(\theta)}$ exist in some neighbourhood of 0 as well\footnote{We use $\Log$ to denote the principal value of the complex logarithm, for which the imaginary part always lies in the interval $(-\pi,\pi]$.}.  From the above, we have
\[
	\Log{F^{(n)}(\varphi)(\theta)} = {\textstyle 2^{n} \psi\left(\frac{\theta}{2^{n}}\right)} 
		+ \sum_{k=1}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}.
\]
We briefly explore what possible limiting values are valid characteristic functions.  We refer to the first term on the left hand side as the \emph{reproduction term} and the remaining sum as the \emph{noise term}, and only consider to the case when both have well-posed limits independent of the other.

\paragraph{Noise Terms}
First, consider the noise terms.  A necessary condition for $\sum_{k=1}^{\infty} 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)$ to converge is that $2^{k} \Psi\left(\frac{\theta}{2^{k}}\right) \to 0$; since $\Psi(0) = 0$, this implies that if it exists, $\Psi'(0+) = 0$.  In particular, as we would expect, if $R$ has a mean, it must be 0.  If, on the other hand, $\Psi(\theta)$ is twice differentiable, so $R$ has mean 0 and finite variance, say $\Psi''(0) = \eta^{2}$, then Taylor's theorem tells us that for $\theta$ sufficiently small, 
\[
	\Psi(\theta) = \frac{\eta^{2}}{2} \theta^{2} + r(\theta)\theta^{2},
\]
where $r(\theta) \to 0$ as $\theta \to 0$.  Thus,
\begin{equation*}
	\frac{\textstyle 2^{k+1} \Psi\left(\frac{\theta}{2^{k+1}}\right)}{\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}
	= \frac{1}{2} \frac{\eta^{2} \theta^{2} + {\textstyle  r\left(\frac{\theta}{2^{k+1}}\right)}\theta^{2}}{\eta^{2} \theta^{2} + {\textstyle  r\left(\frac{\theta}{2^{k}}\right)}\theta^{2}}
	\to \frac{1}{2},
\end{equation*}
as $k \to \infty$ and the sum converges by the ratio test.  In this case,
\begin{align*}
	 \sum_{k=1}^{n-1}  {\textstyle 2^{k} \Psi\left(\frac{\theta}{2^{k}}\right)}
	 &=  \sum_{k=1}^{n-1} 2^{k} {\textstyle \left(- \frac{\eta^{2}}{2}  \frac{\theta^{2}}{2^{2k}}
		+ r\left(\frac{\theta}{2^{k}}\right)\frac{\theta^{2}}{2^{2k}}\right)}\\
	&=- \eta^{2} \theta^{2} (1 - 2^{-n+1})  + \sum_{k=1}^{n-1} {\textstyle r\left(\frac{\theta}{2^{k}}\right)\frac{\theta^{2}}{2^{k}}}
\end{align*}
If we assume that $r(\theta) \equiv 0$, so that the noise is $N(0,\eta^{2})$, then the limiting distribution is $N(0,2\eta^{2})$. When  $r(\theta)$ is non-zero, we don't expect the higher order terms to vanish.

@@

\paragraph{Reproductive Terms:}
We now turn our attention to the limit
\[
		\alpha(\theta) = \lim_{n \to \infty} 2^{n}\psi\left(\frac{\theta}{2^{n}}\right)
\]
If it exists, then for all integers $k$, 
\[
	\alpha(2^{k} \theta) = \lim_{n \to \infty} 2^{n}\psi\left(\frac{2^{k} \theta}{2^{n}}\right) =  \lim_{n \to \infty} 2^{k} 2^{n-k} \psi\left(\frac{\theta}{2^{n-k}}\right) = 2^{k} \alpha(\theta).
\]
and, since $\alpha(0) = 0$,
\[
	\frac{\alpha(\theta)}{\theta} = \frac{\alpha(2^{k} \theta)}{2^{k}\theta} 
	\to \begin{cases} 
		\alpha'(0+) & \text{if $\theta > 0$, and}\\
		\alpha'(0-) & \text{if $\theta < 0$,}
	\end{cases}
\]
as $k \to - \infty$ if the limits exist (\ie there are unique left-and right-hand limits at zero; this is the case if \eg we require $\alpha(\theta)$, and thus $\phi(\theta)$, to be convex functions).  We henceforth assume this.

Since $\varphi(\theta)$ is a characteristic function, it has the Hermitian property: $\phi(-\theta) = \overline{\phi(\theta)}$, and thus $\psi(-\theta) = \overline{\psi(\theta)}$ and $\alpha(-\theta) = \overline{\alpha(\theta)}$.  In particular, if one (and by extension both) limits exist, we must have $\alpha'(0-) = \overline{\alpha'(0+)}$.  In this case, setting $-\gamma + i m = \alpha'(0+)$, we have
\[
	\alpha(\theta) = \begin{cases} 
		i m\theta - \gamma \theta & \text{if $\theta \geq 0$, and}\\
		i m\theta + \gamma \theta & \text{if $\theta < 0$}.
	\end{cases}
\]
If $\gamma > 0$, then we recognize $e^{\alpha(\theta)} = e^{im \theta -\gamma|\theta|}$ as the characteristic function of a Cauchy distribution with median 0 and median absolute deviation $\gamma$, whereas if $\gamma = 0$, then $e^{\alpha(\theta)} = e^{im \theta}$ is the Fourier transform of a Dirac mass at $m$, \ie the characteristic function for a monomorphic population with all individuals having trait value equal to $m$.
(And, $\gamma < 0$ does not give a valid characteristic function.)
% % I think we've shown this characteristic function has to be exp(im\theta - \gamma|\theta|);
% % if $\gamma < 0$ then it is not a characteristic function; am I missing something?
% In general, it does not seem possible to exclude $\gamma < 0$. However, recalling that if $\phi(\theta)$ is the characteristic function of a random variable $Z$, Jensen's inequality tells us that for all $\theta$,
% \begin{equation}\label{eq:CF-J}
% 	|\phi(\theta)| = \left|\E\left[e^{i\theta Z}\right]\right| \leq \E\left[\left|e^{i\theta Z}\right|\right] = 1,
% \end{equation}
% we can conclude $\gamma \geq 0$ when the limiting noise term is a mixture of Gaussians and stable laws of the form \eqref{eq:stablenoises}: we then have 
% \[
% 	|\phi(\theta)| = e^{\re(\alpha(\theta) + o(|\theta|))} = e^{\gamma |\theta| + o(|\theta|))},
% \] 
% and thus is less than or equal to one in a small neighbourhood of $0$ if and only if $\gamma < 0$.

\paragraph{Blending inheritance redux.} 
Note that the characteristic functions constructed above are solutions to \eqref{eq:CF_neutral} when transmission is noiseless, and the offspring have exactly the parental mean trait -- \ie blending inheritance.  The solution $\phi(\theta) = e^{i\theta m}$ is exactly the reversion to the mean that Darwin's detractors used to argue against the theory of evolution \citep{jenkin1867,Provine1971}.  The solution $\phi(\theta) = e^{im \theta -\gamma|\theta|}$ offers an amusing counter-factual: if a Lamarkian population could somehow achieve a Cauchy-distributed trait distribution, it would maintain that diversity indefinitely.

@@

\paragraph{Gaussian Solution:}
First, consider the case when $\mu(x) = e^{a x^{2}}$.   In this case there is a Gaussian solution: suppose $Z$ is Gaussian with mean $m$ and variance $\sigma^{2}$, so
$ \phi(\theta) = \exp(i m \theta - \frac{1}{2} \sigma^{2} \theta^{2}).  $
Moreover, provided $a < \frac{1}{2\sigma^{2}}$, we can explicitly compute $\frac{\mathbb{E}\left[e^{i \theta Z}\mu(Z)\right]}{\mathbb{E}[\mu(Z)]}$: %  using the Gaussian probability density function to conclude that
if $R$ is Gaussian with mean zero and variance $\eta^2$, then equation~\eqref{eqn:MSB_CF} becomes
\[
	e^{i m \theta - \frac{1}{2} \left(\frac{\sigma^{2}}{2} + \eta^{2}\right)\theta^{2}}
	= e^{i \frac{m}{1-2 a \sigma^{2}}\theta 
		- \frac{1}{2} \frac{\sigma^{2}}{1-2 a \sigma^{2}}\theta^{2}},
\]
which, equating real and complex components, has a solution provided $m = 0$ and
\[
	\sigma^{2} = \frac{\sqrt{16 a^{2} \eta^{4} + 24 a \eta^{2}+1} - 4a \eta^{2} -1}{4a} 
	=  2\eta^{2}(1-4a\eta^{2}) + O(a^{2}).
\]

Note that we do not require very weak selection to guarantee a Gaussian steady state, only that $a < \frac{1}{4\eta^{2}}$.  However, this does not imply that the transient distribution is also Gaussian, as is sometimes assumed \citep[e.g.,][]{lande1976natural}. %  The latter does indeed require very weak selection.

@@

Above we have seen that
(a) in principle,
a mutation-selection balance is possible with a Cauchy empirical distribution and Cauchy Mendelian noise,
but (b)
such a model cannot derive from a simple model of additive loci.
To that end, it's instructive to see where the argument of \cite{barton2017infinitesimal} breaks down
if instead of assuming bounded allele effects of order $\Oh(1/\sqrt{M})$,
we assume that the allele at locus $\ell$ in individual $j$ contributes
$\eta^{[j]}_{\ell}/M$, where the $\eta^{[j]}_{\ell}$ are independent $\Cauchy(0,\gamma_{\ell})$ random variables. 
In this case, the typical effect size at locus $\ell$ is of order $\frac{\gamma_{\ell}}{M}$,
which is asymptotically smaller than the allele effects assumed in \cite{barton2017infinitesimal},
but large effect alleles are more likely.

@@

% The key observation is this:
% while is meaningless to speak of variances when the Mendelian sampling term is $\alpha$-stable, if an individual's trait value is informative of the allelic effect at any given locus,
% then its trait value is informative of the \emph{distribution} of an offsprings' trait value,
% and hence there can be no independence between parental traits and the Mendelian sampling term
% that is central to the tractability of the infinitesimal model.

@@

To see what knowing the parental trait value $Z^{[j]}_{M}$ tells us about the contribution of any given locus, $\eta^{[j]}_{\ell}$, we follow the arguments in  \citet{Fisher1918} and \citet{barton2017infinitesimal} using Bayes' Theorem. Proceeding informally, with the probabilities indicating probability density functions, we have 
\begin{align*}
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\} &= \frac{\P\{\eta^{[j]}_{\ell} = y; Z^{[j]} = z\}}{\P\{Z^{[j]} = z\}}\\
        &= \frac{\P\{Z^{[j]} = z\vert\eta^{[j]}_{\ell} = y\}}{\P\{Z^{[j]} = z\}}\P\{\eta^{[j]}_{\ell} = y\}\\
        &=  \frac{\P\{Z^{[j]} -\frac{1}{M} \eta^{[j]}_{\ell} = z - \frac{1}{M} y\}}{\P\{Z^{[j]} = z\}}\P\{\eta^{[j]}_{\ell} = y\}\\
\end{align*}
Now, $Z^{[j]} -\frac{1}{M} \eta^{[j]}_{\ell} = \frac{1}{M} \sum_{k = 1 : k \neq i}^{M} \eta^{[j]}_{k}$ is Cauchy-distributed with scale $\bar{\gamma} - \frac{\gamma_{\ell}}{M}$.  Using the probability density function for a Cauchy distributed random variable \eqref{eq:Cpdf}, a straightforward computation gives
\begin{align*}
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\}
    &=
    \frac{f\left(z - \frac{y}{M} ;0,\bar{\gamma}-\frac{\gamma_{\ell}}{M}\right)}{f(z;0,\bar{\gamma})} \P\{\eta^{[j]}_{\ell} = y\}\\
    &=
    \left(1
        +
        \frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})}
        \frac{1}{M}
        + \Oh\left(\frac{1}{M^{2}}\right)\right)
        \P\{\eta^{[j]}_{\ell} = y\}.
\end{align*}
Noting that $|(\bar{\gamma}^2 - z^2)/(\bar{\gamma}^2 + z^2)| \le 1$
and $|z/(\bar{\gamma}^2 + z^2)| \le 1/(2 \bar{\gamma})$
(since it is maximized at $z = \bar{\gamma}$),
so
\begin{align*}
        \left|
        \frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})}
        \right|
        \le \frac{|y|}{\gamma_\ell \bar{\gamma}} ,
\end{align*}
% Now, as $z \to 0$,
% $\frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})} \to \frac{\gamma_{\ell}}{\bar{\gamma}}$
% and as $z \to \pm \infty$,
% $\frac{\gamma_{\ell}(\bar{\gamma}^{2}-z^{2})+2zy}{\gamma_{\ell}(\bar{\gamma}^{2}+z^{2})} \to -\frac{\gamma_{\ell}}{\bar{\gamma}}$,
% \comment{I'm not sure where $\gamma_\ell$ went here}
% whereas $|\frac{\bar{\gamma}^{2}-z^{2}+2zy}{\bar{\gamma}^{2}+z^{2}}|$ 
% \[
% 	\frac{(\gamma_{\ell}^{2}+y^{2})\left(\sqrt{\gamma_{\ell}^{2}+y^{2}}-\gamma_{\ell}\right)}{\bar{\gamma}(\gamma_{\ell}^{2}+y^{2} - \gamma_{\ell}\sqrt{\gamma_{\ell}^{2}+y^{2}})},
% \]
% which is asymptotically equal to $\frac{|y|}{\bar{\gamma}}$ for large values of $|y|$, at
% \[
% 	z = -\frac{\bar{\gamma}}{y}(\gamma_{\ell} \pm \sqrt{\gamma_{\ell}^{2}+y^{2}}),  
% \]
% which is itself asymptotically equal to $\mp \sgn(y) \bar{\gamma}$ for large values of $|y|$.
we have that
\[
    \left|
    \P\{\eta^{[j]}_{\ell} = y \vert Z^{[j]} = z\} - \P\{\eta^{[j]}_{\ell} = y\}
    \right|
    \le \left(\left(1 + \frac{|y|}{\gamma_\ell \bar{\gamma}}\right) \frac{1}{M} + \Oh\left(\frac{1}{M^2}\right)\right)  \P\{\eta^{[j]}_{\ell} = y\}.
\]
% Unlike the case of bounded allelic effects, the bound is independent of the trait value $Z^{[j]}$. 
In the case of bounded allelic effects, the error introduced by approximating the effect-size distribution conditional on the trait value by the unconditioned distribution is proportional to $|Z^{[j]}|$, so that extreme trait values are most informative of the size of allelic effects,
whereas here,
the bound is independent of the trait value,
and the error is maximized when the trait value is approximately equal to
the mean absolute deviation of its distribution, \ie the median value of $|Z^{[j]}|$.

@@

\begin{figure}
    \begin{center}
        \includegraphics{sims/neutral_seg_noise}
    \end{center}
    \caption{
        The distribution of Mendelian sampling terms
        with Gaussian \textbf{(A-C)} and Cauchy \textbf{(D-F)} effect size distributions,
        from the same simulations shown in Figure~\ref{fig:trait_distrns},
        for all individuals born during the last 1,000 time units of the simulation.
        \textbf{(A,D)} Mendelian noise (offspring trait minus midparent) plotted against midparent.
        \textbf{(B,E)} Histograms of the Mendelian sampling term.
        \textbf{(B,E)} Enrichment in quantiles of the Mendelian sampling term conditional on midparent value.
        To compute the latter,
        let $q_0, q_2, q_4, \ldots, q_{98}, q_{100}$ divide the distribution of the Mendelian sampling term
        into 50 bins with roughly equal numbers in each (i.e., the quantiles),
        let $p_k(a,b)$ denote the proportion of the offspring of parents with midparent value
        is in $[a, b)$ whose Mendelian sampling term is in $[q_{k-1}, q_k)$,
        and let $p_k$ be the proportion of all offspring with Mendelian noise in $[q_{k-1}, q_k)$
        (so, $p_k \approx 0.02$).
        Then, each line shows $p_k(a,b)/p_k$
        plotted against the midpoint of the corresponding quantile bin $(q_{k-1},q_k)$,
        for $(a,b)$ chosen to span the 5\% of midparents centered on:
        (red) the 10\% quantile,
        (black) the median, and
        (green) the 90\% quantile of midparent value.
        \label{fig:seg_noise}
    }
\end{figure}
